---
title: BioSIDS
subtitle: "**Biostatistics | Bioinformatics | Bio-Data Science**"
format: 
  html: 
    toc: true
    embed-resources: true
    page-layout: full
    fig-dpi: 300
---

Innovative Data Science for Global Health Challenges

```{r}
#| warning: false
#| echo: false
# create projects
require(here)
require(stringr)
require(tidyverse)
```

:::::: columns
:::: {.column width="70%"}
::: columns
### Welcome to the Bio3SIDS
:::


BioSIDS Department leverages cutting-edge statistical methods to empower studies.\
Our data-driven insights help shape strategies that combat some of the most urgent public health issues.

**Explore Our Core Services**

-   **Study Design**: Crafting the blueprint for rigorous research.
-   **Data Management**: Ensuring the integrity and security of vital research data.
-   **Statistical Analysis**: Transforming raw data into actionable insights.
-   **Results Dissemination**: Communicating findings to inform public health policies.

**Engage with Us**

-   [Collaborate](#) with our experts on your next project.
-   [Join Our Team](#) and make a difference.

**Stay Updated** - [Subscribe](#) to our newsletter for the latest updates and breakthroughs.

**Contact Us** - [biosids@dataaidconsultanting.com](mailto:biosids@dataaidconsultanting.com)
::::

::: {.column width="20%"}
### Our Team is Involved every step of the way {.centering}

```{r fig.width=5, fig.height=6}
#| warning: false
#| echo: false
# Load necessary libraries

# Define the workflow steps and their connections
workflow_steps <- data.frame(
  step = c("Problem Definition", "Study Design", "Data Collection", "Data Management",
           "Preliminary Data Analysis", "Statistical Analysis", "Results Interpretation",
           "Results Dissemination", "Documentation"),
  y = c(9:1),
  x = c(1, 1, 1, 1, 1, 1, 1, 1, 1),
  color = c(
    "#42B540FF", "#0099B4FF", "#E99714FF", "#ED3000FF", '#20854EFF',
    "#00468BFF", "#0072B5FF", "#FDAF91FF", "#BC3C29FF")
)

# Create the base plot
p <- ggplot(
   workflow_steps, aes(x = x, y = y, label = step, fill = color)) +
  geom_label(aes(x=x-1),size = 9,hjust='left',color='white',fontface='bold') +  # Add labels above the points
  geom_text(aes(x=2,y=1,label=''),size = 9,hjust='right',color='white') +  # Add labels above the points
  geom_point(aes(x=x-1), size = 6) +  # Add points with custom colors
  scale_color_identity() +  # Use colors as provided
  theme_minimal() +
   geom_segment(
     aes(x = 0, y = 1, xend = 0, yend = max(workflow_steps$y),
         fill = I(color)), size = 1.5)+
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        legend.position = "none",  # Hide legend
        panel.grid = element_blank())  # Remove grid
p

```
:::
::::::